---
title: "Text Analysis Demo"
author: "Akitaka Matsuo"
institute: "Institute for Data Science and Analytics, University of Essex"
date: "15-02-2022"
output: 
  ioslides_presentation:
    smaller: true
    widescreen: true
    transition: faster
---



```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(knitr)
```


## Today's schedule

1. Install required software
1. Read data into R
2. Convert R data to quanteda format
3. Text Analysis with quanteda: Descriptive statistics
4. Text Analysis with quanteda: Estimating models
5. Estimating Glove




## Required software

-	R, RStudio
- r-packages
  - tidyverse
  - quanteda (https://quanteda.io/articles/pkgdown/quickstart_ja.html)
    - quanteda.textmodels
    - quanteda.textstats
    - quanteda.textplots
  - caret (machine learning utility)
  - e1071 (confusionMatrix function)
  - text2vec (word embedding)
  - stringi (general text processing)

## Download data and slides

- All the files used in this workshop are compiled in this github repository
    https://github.com/amatsuo/HEROES-2022-TextAnalysis
- In RStudio, click on the project icon
    - New Project]->[Version Control]->[Git]
    - Enter the URL above


## Packages

1. tidyverse
    - https://www.tidyverse.org/
    - "The tidyverse is an opinionated collection of R packages designed for data science."
    - To install
    ```{r eval=FALSE}
    install.packages("tidyverse")
    ```
2. quanteda
    - R package for integrated text analysis
    - To install
    ```{r eval=FALSE}
    install.packages("quanteda", "quanteda.textplots", "quanteda.textmodels", 
                     "quanteda.textstats")
    ```` 

3. other
    ```{r eval=FALSE}
    install.packages(c("caret", "e1071", "DT", "text2vec", "stringi"))
    ````


## Load text data into R

**Load the packages**

```{r message=FALSE}
library(tidyverse)
library(quanteda)
library(quanteda.textmodels)
library(quanteda.textstats)
library(quanteda.textplots)
library(stringi)
library(caret)
library(DT)
```


## Load text data into R

- All the data is in the `data` folder
- This is the IMF and AMRO country reports extracted from pdf

**Let's list the files first**

````{r}
list.files("data", pattern = "csv")
````

- 11 files, file name with the convention `{InternationalOrganization}-{Country}-{year}.csv`


## Load text data into R

### Check the contents of the file

```{r message=FALSE}
data_temp <- read_csv("data/AMRO-Korea-2018.csv") # Open the data
print(data_temp) # Print it to the screen
```

The pre-processed pdfs of the report are in their respective files. From here, we can remove the unnecessary rows and columns and extract the necessary variables

## Load text data into R

### Data Processing

- Variables to use are `page_number, paragraph_number, text`.
- To delete a line, use the value of the variable `pages_to_skip, detection`.

**Processing dataframes with `dplyr`**.
````{r}
# Comments after "#".

data_temp <- data_temp %>% # "%>%" is dplyr's pipe
  filter(pages_to_skip != TRUE) %>% # filter rows. Remove pages to skip.
  filter(detection == "normal") %>% # select lines with normal text
  select(page_number, paragraph_number, text)
print(data_temp)

````



## Load text data into R
### Batch processing of many files

Putting all these processes together into a single data frame
Here are three ways to do it

##### Method 1: Use a for loop (don't)

````{r message=FALSE}
data_all <- NULL # create empty data
file_names <- list.files("data", pattern = "csv", full.names = TRUE)

for (fn in file_names) {
  data_current <- read_csv(fn) # open a file
  data_current <- data_current %>% 
    filter(pages_to_skip != TRUE) %>% 
    filter(detection == "normal") %>% 
    select(page_number, paragraph_number, text) %>%
    mutate(file_name = fn)
  data_all <- bind_rows(data_all, data_current) 
}

````

## Load text data into R
##### Method 2: map() + bind_rows() (or map_dfr())

```{r message=FALSE}
file_names <- list.files("data", pattern = "csv", full.names = TRUE)

data_all_2 <- file_names %>%
  map(~read_csv(.x) %>% 
    filter(pages_to_skip != TRUE) %>%
    filter(detection == "normal") %>%
    select(page_number, paragraph_number, text) %>%
    mutate(file_name = .x)) %>% bind_rows()
```

## Load text data into R
### Method 3: use `readtext`


```{r}
library(readtext)
data_all_3 <- 
  readtext("data", text_field = "text") %>% 
  filter(pages_to_skip != TRUE) %>% 
  filter(detection == "normal") %>% 
  select(doc_id, page_number, paragraph_number, text) %>%
  rename(file_name = doc_id)
```


## Load text data into R
#### Extracting variables from file names

Since the data we have created so far does not contain country names, etc., we will extract them from the variables in the file name.

```{r}
data_all <- 
  data_all %>%
  # Create tmp temporary variable
  mutate(tmp = file_name %>%
           stri_replace_first_fixed("data/", "") %>%
           stri_replace_first_fixed(".csv", "")) %>% # remove extraneous parts
  separate(tmp, sep = "-", into = c("institution", "country", "year")) 
　# Use dplyr's separate() to split the tmp column into three variables
```



## Convert R data to quanteda format

With quanteda, you can easily convert R data frames into a form that can be used for data analysis.

**Steps**.

1. Create a corpus
2. Tokenize the text
3. Create a document feature matrix (DFM)

## Creating a corpus

A **corpus** is an object of **quanteda** that stores texts and a set of meta-variables of the text together, and can be easily created from an R dataframe. The texts are usually not modified before the corpus is created, but the corpus of paragraphs can be divided into sentences at this stage.

```{r}
data_corpus <- corpus(data_all, text_field = "text")
print(data_corpus)
```

Use `as.character()` to check the contents
```{r}
as.character(data_corpus) %>% head(2) %>% print()
```


### Extracting document variables

A corpus created from a dataframe with `corpus()` retains all variables, and they are inherited even if you tokenize or create a dfm. Use the `docvars()` command to extract them.

```{r}
docvars(data_corpus) %>% head()
```

## Corpus Transformation

`quanteda` provides a method for remaking a corpus in the form of `corpus_*()`.

#### Changing text units

From paragraphs to sentence units.

```{r}
data_corpus_sentence <- corpus_reshape(data_corpus, to = 'sentences')
print(data_corpus_sentence)
```

#### Selecting part of a corpus

The second argument of `corpus_subset()` specifies the condition for selecting a corpus. You can use document variables directly.

```{r}
data_corpus_korea <- corpus_subset(data_corpus, country == 'Korea')
print(data_corpus_korea)
```


## Tokenization

**quanetda** uses the `tokens()` command to tokenize text. There are various units of tokens, but usually words are used as a unit.

```{r}
data_tokens <- tokens(data_corpus)
data_tokens[1]
```

## Removing unnecessary tokens, reshaping tokens

In the process of creating a `tokens()` object, or after it has been created, you can format the tokens as needed.

All options are basically turned off by default, but you can turn them on to perform various operations.

```{r}
tokens_temp <- tokens(data_corpus,
                      remove_numbers = FALSE, 
                      remove_punct = FALSE,
                      remove_symbols = FALSE, 
                      remove_separators = TRUE,
                      remove_twitter = FALSE, 
                      remove_hyphens = FALSE, 
                      remove_url = FALSE)
```


Or you can use `tokens_select()` for more fine-grained operations.

```{r}
long_tokens <- tokens_select(data_tokens, min_nchar = 3)
number_tokens <- tokens_select(data_tokens, "^\\d", valuetype = "regex")
```

## KeyWord-In-Context (kwic)

By applying kwic to **tokens** objects, you can extract the contexts in which words of interest to you are used. For example, "inflation targeting".

```{r}
kwic(data_tokens, phrase("inflation targe*")) 
```

## Create a tokens object for the purpose of this analysis


```{r}
data_tokens_final <- tokens(data_corpus,
                      remove_numbers = TRUE, 
                      remove_punct = FALSE,
                      remove_symbols = FALSE, 
                      remove_separators = TRUE,
                      split_hyphens = FALSE, 
                      remove_url = TRUE) %>%
  tokens_remove(pattern = stopwords(), padding = TRUE) %>% # remove stopwords
  tokens_remove(pattern = c("AMRO", "IMF"), padding = TRUE) %>% # remove institution name
  tokens_remove(pattern = c("Indonesia*", "Japan*", "Korea*", "Thai*", "Vietnum*"),
                padding = TRUE) %>% # remove country names
  tokens_keep(pattern = "^[a-zA-Z]+$", valuetype = "regex", padding = TRUE) # Keep words made of only alphabetic characters

data_tokens_final[1]
```

## Find the collocation

Try calculating the collocation

```{r}
colloc <- textstat_collocations(data_tokens_final, min_count = 5, tolower = FALSE)
colloc %>% 
  filter(collocation %>% stri_trans_tolower %>% stri_detect_fixed("inflation"))
```

## "stability"

```{r}
colloc %>% 
  filter(collocation %>% stri_trans_tolower %>% stri_detect_fixed("stability"))
```

## Use of collocation

There are many possible ways to use this, but one way is to concatenate a collocation and use this in subsequent analysis.

```{r}
colloc <- colloc %>% filter(z > 3)
data_tokens_compounded <- tokens_compound(data_tokens_final,
                                          pattern = phrase(colloc$collocation)) %>%
  tokens_remove("*consultation_report*")
```

## Create a dfm

Using the tokens object created so far, create a document feature matrix (dfm) for later analysis. A dfm is a matrix where each document is a row and each feature (e.g. word) is a column.


```{r}
data_dfm <- dfm(data_tokens_compounded, tolower = TRUE) %>% 
  dfm_select(min_nchar = 3) # Remove words with less than 3 characters.
data_dfm
```

Furthermore, erase words that only appear in one document or that have not been used more than 10 times.

```{r}
data_dfm <- dfm_trim(data_dfm, min_docfreq = 2, min_termfreq = 10) 
data_dfm
```

# Text analysis with quanteda: Descriptive statistics

## Competing expectations

**1. (globalist complementarity): AMRO is as neoclassical as IMF**

**2. (developmental state hypothesis): AMRO is more developmentalist than IMF**


## Commonly used words

First, let's simply check what words are used.

```{r}
topfeatures(data_dfm, n = 30)
```

## Check keyness

Use `textstat_keyness()` to compare the difference between feature words used in AMRO and IMF.

### Keywords for AMRO

```{r}
textstat_keyness(data_dfm, target = docvars(data_dfm, "institution") == "AMRO") %>% head(20)
```

## Check keyness

### Keywords for  IMF

```{r}
textstat_keyness(data_dfm, target = docvars(data_dfm, "institution") == "IMF") %>% head(20)
```

## Check keyness: keywords derived from expectations

The following list of words were provided as words that might be related to each hypothesis. Let's feed the words that we are interested in on the next page.

**Globalist Hypothesis:** equilibrium, inflation targeting, currency volatility, fiscal stability, credibility, output gap, balanced growth, safety net, market economy, macro-prudential, capital adequacy, competition, debt sustainability

**Regional-developmentalist Hypothesis:** autonomy, capital accumulation, currency appreciation, fiscal stimulus, strategy, output growth, dynamic growth, competitiveness, state control, saving, investment, concentration, current account surplus


## Check keyness

```{r}
textstat_keyness(data_dfm, target = docvars(data_dfm, "institution") == "AMRO") %>%
  mutate_at(.vars = 2:3, round, digits = 3) %>%
  datatable()
```



# Text analysis with quanteda: analysis with models

## Overview

In the following, we explain how to use the `textmodel_*`  functions provided by **quanteda.textmodel**.

It estimates and interprets the following two models: 

1. naive bayes model
2. wordfish model

## Classify using the Naive Bayes Model

- Supervised learning model
- Linear model so we can check the score of each word

**This example**.

- "AMRO", "IMF" labels are outputs.
- The unit of analysis is each paragraph of the report
- What to check
    - Is it possible to classify the words based on their use in the first place?
    - If so, what words are influencing it?
- To avoid overlearning problems, separate the data into train and test.

## Use Naive Bayes Model for classification

```{r}
# shuffle dfm
set.seed(20190924)
data_dfm <- dfm_sample(data_dfm)

# train-test split
train <- sample(nrow(data_dfm), size = nrow(data_dfm) * 0.7)
train <- seq(nrow(data_dfm)) %in% train

# split dfm
data_dfm_train <- dfm_subset(data_dfm, subset = train)
data_dfm_test <- dfm_subset(data_dfm, subset = !train)

# estimate the model
model_nb <- textmodel_nb(data_dfm_train, docvars(data_dfm_train, "institution") == "AMRO")
```

## Naive Bayes
```{r}
train_pred <- predict(model_nb)
train_truth <- docvars(data_dfm_train, "institution") == "AMRO"
table(train_pred, train_truth)
```

```{r}
test_pred <- predict(model_nb, newdata = data_dfm_test)
test_truth <- docvars(data_dfm_test, "institution") == "AMRO"
table(test_pred, test_truth)

```

## Naive Bayes, Train Confusion Matrix
```{r}
confusionMatrix(train_pred, factor(train_truth))
```

## Naive Bayes, Test Confusion Matrix

```{r}
confusionMatrix(test_pred, factor(test_truth))
```

## Naive Bayes, checking for words

## Prepare word data

```{r}
coef_prob <- coefficients(model_nb)[, 2] %>% data.frame() %>% 
  rename(prob1 = ".") %>% rownames_to_column() %>%
  mutate(count =  data_dfm_train %>% colSums())
```

## Naive Bayes, word table

```{r}
coef_prob %>% 
  filter(nchar(rowname) >=2) %>%
  filter(count > quantile(count, .7)) %>% # keep top thirty words
  arrange(-prob1) %>% mutate(prob1 = round(prob1, 3)) %>% 
  datatable() 
```

## Scaling with Wordfish

As an example of unsupervised learning, we estimate the wordfish model.

**This example**.

- Unit of analysis is the report level
- Estimate the position of the report
- Since this is unsupervised learning, you need to interpret the meaning of the axes by yourself.



## Scaling with Wordfish

```{r}
# Create a new document variable "report".
docvars(data_dfm, "report") <- paste(docvars(data_dfm, "institution"),
                                     docvars(data_dfm, "country"),
                                     docvars(data_dfm, "year")) 
# Use report to aggregate dfm to report level
data_dfm_report <- dfm_group(data_dfm, groups = report)
# Estimate the model
model_wf <- textmodel_wordfish(data_dfm_report)
````

## Wordfish: plotting positions

```{r}
textplot_scale1d(model_wf)
```


## Wordfish: plot words

```{r}
textplot_scale1d(model_wf, margin = 'features')
```

## Wordfish: word table

```{r}
coefs <- coefficients(model_wf)$features %>%
  as.data.frame() %>% rownames_to_column(var = "feature") %>%
  mutate_at(2:3, round, digits = 3) %>% arrange(-beta)
datatable(coefs)
```

## Other things you can do with quanteda

- Estimating topic models
  - Use `convert()` function and fit a model
    - `topicmodels` and `stm`
- Estimating word vectors
  - `word2vec` (R package)
  - Or call python based packages through `reticulate`